Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Updated

Note that  when a reachability-based  collector visits a cell  for the
first time,  it is  marked.  Explorations starting  from the  cell are
curtailed if the cell is  visited subsequently due to sharing. This is
because the collector can assume  that the region of the heap starting
from  the  cell has  already  been  explored.  Since a  liveness-based
collector may  reach the cell each  time with a  different state, this
curtailment cannot  be done in  the case of  LGC. This is  an inherent
drawback  of a  liveness-based collector.   This can  be  mitigated by
maintaining a list of liveness  automata states that a particular heap
cell was traversed with and  ensuring that we do not repeat traversals
if we reach the cell in one of these states.

>>>>

Note that  when a reachability-based  collector visits a cell  for the
first time,  it is  marked.  Explorations starting  from the  cell are
curtailed if the cell is visited subsequently due to sharing.  Since a
liveness-based collector may reach the  same cell multiple times, each
time with a different automaton state, this curtailment cannot be done
in the case  of LGC. This is an inherent  drawback of a liveness-based
collector.  This  can be mitigated  by maintaining a list  of liveness
automata states  that a  particular heap cell  was traversed  with and
avoid repeated traversals if we reach the cell in one of these states.
